---
title: "GWAS Report"
author: "Contact:<a target = '_blank'>SAGA</a> r.a.pacheco@cgiar.org"
date: "`r format(Sys.time(), '%B %d, %Y')`"  
output: html_document
params:
  toDownload: FALSE
  resGWAS : NULL
  qqplotR : NULL
  qtlplotR : NULL
  manplotR : NULL
  rengenplotR : NULL
---
  
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(dependson = knitr::all_labels(),
                      echo = FALSE,
                      cache = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      comment = NA,
                      out.width = "100%",
                      error = TRUE)
options(knitr.kable.NA = '')
# loading necessary R packages ####
## data manipulation
# library(dplyr)    # %>%, data cleaning functions
library(magrittr) # coerce col to factors or numeric
## outputs - graphs, tables
library(ggplot2)  # ggplot(), etc.
library(plotly)  # ggplot(), etc.
library(DT)       # datatable()
library(knitr)    # kable
library(data.table)
library(shiny)
```

```{r printfxn, include=FALSE}
# functions ####
# for printing tables (data.frames) - DT::datatable()
printTable <- function(DT, pageLength = 10, 
                         numericColNames = NULL, numRound = 3, 
                         scrollXOpt = FALSE, colNames = NULL, autoWidthOpt = FALSE,...) {
    
    DT <- data.frame(lapply(X = DT, 
                            FUN = function(x) {
                              if(is.numeric(x)){
                                round(x, numRound)
                              } else {
                                x
                              }
                            }))
    
    table <- DT::datatable(data = DT, 
                           colnames = colNames,
                           filter = "top", 
                           options = list(autoWidth = autoWidthOpt,
                                          dom = 'l<<t>pB>', 
                                          buttons = c('copy', 'csv', 'excel', 'print'),
                                          pageLength = pageLength,
                                          searchHighlight = TRUE,
                                          lengthMenu = list(c(10, 20, 30, 40, 50,-1),c("10", "20", "30", "40", "50","All")),
                                          scrollX = scrollXOpt),
                           extensions = 'Buttons',
                           rownames = FALSE,
                           ...)
    if (length(numericColNames) > 0){
      table <- table %>% DT::formatRound(columns = numericColNames,
                                     digits = numRound)
    }
    
    table
  }
```

```{r, include=FALSE}
# Init Step to make sure that the dependencies are loaded
htmltools::tagList(printTable(mtcars))
htmltools::tagList(ggplotly(ggplot()))
# Get the current figure size in pixels:
get_w <- function() {
  with(knitr::opts_current$get(c("fig.width", "dpi", "fig.retina")),
       fig.width*dpi/fig.retina)
}

get_h <- function() {
  with(knitr::opts_current$get(c("fig.height", "dpi", "fig.retina")),
       fig.height*dpi/fig.retina)
}
```

### QQPlot
  
  In this QQ plot, most points closely follow the diagonal line, indicating that the observed distribution of p-values is consistent with the null hypothesis. 
  The deviation at the upper tail suggests the presence of significant associations that may correspond to true QTLs. If the lambda value is greater than 1, then this may be evidence for some systematic bias that needs to be corrected in your analysis.

<p>&nbsp;</p>
```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))	
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	
if("params" %in%ls()){ # we will download the document
	p=params$qqplotR
	p
}else{
	shiny::renderPlot({
	p=params$qqplotR	
	p
})
}
```

<p>&nbsp;</p>

### QTL Plot
  
  This plot illustrates the association between genomic regions and the trait of interest using LOD (logarithm of odds) scores. The x-axis represents the genomic position across chromosomes, while the y-axis displays the evaluated traits. 
  Each point corresponds to a detected QTL, where its position reflects the genomic location and the trait it influences. The color of the points indicates the direction of the allelic effect:
  blue points represent negative allelic effects, while green points indicate positive allelic effects on the trait. The size of each point is proportional to the magnitude of the allelic effect, where larger points indicate stronger effects and smaller points represent weaker effects.
  Higher LOD values provide stronger statistical evidence for the presence of a QTL, and regions with prominent signals may represent candidate loci influencing the trait.

<p>&nbsp;</p>
```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))	
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	
if("params" %in%ls()){ # we will download the document
	p=params$qtlplotR
	p
}else{
	shiny::renderPlot({	
	p=params$qtlplotR	
	p
})
}
```

<p>&nbsp;</p>

### Manhathan Plot
  
  The Manhattan plot shows the genomic distribution of marker–trait associations. Each point represents a marker, and peaks indicate regions with strong evidence of association.This plot allows the user to visualize the significant markers.

<p>&nbsp;</p>
```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))	
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	
if("params" %in%ls()){ # we will download the document
	p=params$manplotR
	p
}else{
	shiny::renderPlot({	
	p=params$manplotR	
	p
})
}
```

<p>&nbsp;</p>

### Marker effects
  
This table summarizes the results of the genome-wide association study (GWAS) for the analyzed traits. Each row corresponds to a genetic marker (SNP) evaluated for its association with a specific trait.  

The columns are defined as follows:

- **trait**: The phenotype or trait analyzed.  
- **snp**: The identifier of the single nucleotide polymorphism (SNP).  
- **chr**: The chromosome where the SNP is located.  
- **pos**: The physical position of the SNP on the chromosome.  
- **allFreq**: The allele frequency of the SNP in the studied population.  
- **pValue**: The statistical significance of the association between the SNP and the trait. Lower values indicate stronger evidence of association.  
- **effect**: The estimated effect size of the SNP on the trait.  
- **effectSe**: The standard error of the estimated effect, indicating the precision of the estimate.  
- **RLR2**: The proportion of phenotypic variance explained by the SNP.  
- **LOD**: The logarithm of odds score, representing the strength of evidence for the association.  

SNPs with low p-values, high LOD scores, and larger effect sizes are considered strong candidates for influencing the trait.

<p>&nbsp;</p>
```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))
  }else{
    load("result.RData")	
  }
}, error = function(e) {
  shinyjs::hide()
}))
		GWASDrops<-params$resGWAS[[1]]
		ass=split(GWASDrops[["GWAResult"]][["dropsPheno"]],GWASDrops[["GWAResult"]][["dropsPheno"]][["trait"]])
		ass=do.call(rbind,ass)
    
if("params"%in%ls()){ # we will download the document
	printTable(ass, autoWidthOpt = TRUE, scrollXOpt = FALSE,colNames = colnames(ass))           
  }else{    
    DT::renderDT(printTable(ass, colNames = colnames(ass),
                        autoWidthOpt = FALSE, scrollXOpt = TRUE), server = FALSE)
  }
  
```


<p>&nbsp;</p>

### Regional associated gene plot
  
  This plot allows the user to visualize the associated genes in the region that they selected.

<p>&nbsp;</p>
```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))	
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	
if("params" %in%ls()){ # we will download the document
    if (!is.null(params$rengenplotR[[1]])){
		IntReg=params$rengenplotR[[1]]
		print(IntReg)	
	}else{
		plot.new()
        text(0.5, 0.5, "Nothing to show", cex = 1.5)
	}
}else{
	shiny::renderPlot({
	if (!is.null(params$rengenplotR[[1]])){
		IntReg=params$rengenplotR[[1]]
		print(IntReg)	
	}else{
		plot.new()
        text(0.5, 0.5, "Nothing to show", cex = 1.5)
	}
})
}
```

### Regional associated gene table  

<p>&nbsp;</p>

```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))   
  }else{
    load("resultPopStr.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	if (!is.null(params$rengenplotR[[2]])){	
		seemds=as.data.frame(params$rengenplotR[[2]])	
	}else{ seemds=data.frame(Mensaje = "Nothing to show")}
	
	if("params" %in%ls()){ # we will download the document
	  printTable(seemds, autoWidthOpt = TRUE, scrollXOpt = FALSE,colNames = colnames(seemds))
	}else{
	  DT::renderDT(printTable(seemds,colNames = colnames(seemds),
                        autoWidthOpt = FALSE, scrollXOpt = TRUE), server = FALSE)
	}    

```







