---
title: "CoreSubset Report"
author: "Contact:<a target = '_blank'>SAGA</a> r.a.pacheco@cgiar.org"
date: "`r format(Sys.time(), '%B %d, %Y')`"  
output: html_document
params:
  toDownload: FALSE
  resCore: NULL
  mds2: NULL  
---
  
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(dependson = knitr::all_labels(),
                      echo = FALSE,
                      cache = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      comment = NA,
                      out.width = "100%",
                      error = TRUE)
options(knitr.kable.NA = '')
# loading necessary R packages ####
## data manipulation
# library(dplyr)    # %>%, data cleaning functions
library(magrittr) # coerce col to factors or numeric
## outputs - graphs, tables
library(ggplot2)  # ggplot(), etc.
library(plotly)  # ggplot(), etc.
library(DT)       # datatable()
library(knitr)    # kable
library(data.table)
library(shiny)
```

```{r printfxn, include=FALSE}
# functions ####
# for printing tables (data.frames) - DT::datatable()
printTable <- function(DT, pageLength = 10, 
                         numericColNames = NULL, numRound = 3, 
                         scrollXOpt = FALSE, colNames = NULL, autoWidthOpt = FALSE,...) {
    
    DT <- data.frame(lapply(X = DT, 
                            FUN = function(x) {
                              if(is.numeric(x)){
                                round(x, numRound)
                              } else {
                                x
                              }
                            }))
    
    table <- DT::datatable(data = DT, 
                           colnames = colNames,
                           filter = "top", 
                           options = list(autoWidth = autoWidthOpt,
                                          dom = 'l<<t>pB>', 
                                          buttons = c('copy', 'csv', 'excel', 'print'),
                                          pageLength = pageLength,
                                          searchHighlight = TRUE,
                                          lengthMenu = list(c(10, 20, 30, 40, 50,-1),c("10", "20", "30", "40", "50","All")),
                                          scrollX = scrollXOpt),
                           extensions = 'Buttons',
                           rownames = FALSE,
                           ...)
    if (length(numericColNames) > 0){
      table <- table %>% DT::formatRound(columns = numericColNames,
                                     digits = numRound)
    }
    
    table
  }
```

```{r, include=FALSE}
# Init Step to make sure that the dependencies are loaded
htmltools::tagList(printTable(mtcars))
htmltools::tagList(ggplotly(ggplot()))
# Get the current figure size in pixels:
get_w <- function() {
  with(knitr::opts_current$get(c("fig.width", "dpi", "fig.retina")),
       fig.width*dpi/fig.retina)
}

get_h <- function() {
  with(knitr::opts_current$get(c("fig.height", "dpi", "fig.retina")),
       fig.height*dpi/fig.retina)
}
```

### Summary diversity comparison

The following table allows you to inspect the principal statistics for the diversity analysis.

<p>&nbsp;</p>

```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))   
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
	
    seedatosum<-as.data.frame(params$resCore[[2]])
if("params"%in%ls()){ # we will download the document
  printTable(seedatosum, autoWidthOpt = TRUE, scrollXOpt = FALSE)           
  }else{    
    DT::renderDT(printTable(seedatosum,
                        autoWidthOpt = FALSE, scrollXOpt = TRUE), server = FALSE)
  }
  
```
<p>&nbsp;</p>

### MDS table with genotypes selected in the Core

<p>&nbsp;</p>

```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))   
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
	
    seedatosum<-as.data.frame(params$resCore[[1]] )
if("params"%in%ls()){ # we will download the document
  printTable(seedatosum, autoWidthOpt = TRUE, scrollXOpt = FALSE,colNames = colnames(seedatosum))           
  }else{    
    DT::renderDT(printTable(seedatosum,
                        autoWidthOpt = FALSE, scrollXOpt = TRUE,colNames = colnames(seedatosum)), server = FALSE)
  }
  
```

<p>&nbsp;</p>

### Multidimensional scaling plot 2D
  
  This plot allows the user to visualize the closeness or distance between genotypes to check if the population structure was as expected.

<p>&nbsp;</p>
```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))	
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	
if("params" %in%ls()){ # we will download the document
	p=params$mds2
	p
}else{
	plotly::renderPlotly({		
	p=params$mds2	
	p
})
}
```