---
title: "Biodiversity Report"
author: "Contact:<a target = '_blank'>SAGA</a> r.a.pacheco@cgiar.org"
date: "`r format(Sys.time(), '%B %d, %Y')`"  
output: html_document
params:
  toDownload: FALSE
  dend: NULL
  mds2: NULL
  mds3: NULL
  heat: NULL
  amovaT: NULL
  popstr: NULL
  summBio: NULL
---
  
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(dependson = knitr::all_labels(),
                      echo = FALSE,
                      cache = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      comment = NA,
                      out.width = "100%",
                      error = TRUE)
options(knitr.kable.NA = '')
# loading necessary R packages ####
## data manipulation
# library(dplyr)    # %>%, data cleaning functions
library(magrittr) # coerce col to factors or numeric
## outputs - graphs, tables
library(ggplot2)  # ggplot(), etc.
library(plotly)  # ggplot(), etc.
library(DT)       # datatable()
library(knitr)    # kable
library(data.table)
library(shiny)
```

```{r printfxn, include=FALSE}
# functions ####
# for printing tables (data.frames) - DT::datatable()
printTable <- function(DT, pageLength = 10, 
                         numericColNames = NULL, numRound = 3, 
                         scrollXOpt = FALSE, colNames = NULL, autoWidthOpt = FALSE,...) {
    
    DT <- data.frame(lapply(X = DT, 
                            FUN = function(x) {
                              if(is.numeric(x)){
                                round(x, numRound)
                              } else {
                                x
                              }
                            }))
    
    table <- DT::datatable(data = DT, 
                           colnames = colNames,
                           filter = "top", 
                           options = list(autoWidth = autoWidthOpt,
                                          dom = 'l<<t>pB>', 
                                          buttons = c('copy', 'csv', 'excel', 'print'),
                                          pageLength = pageLength,
                                          searchHighlight = TRUE,
                                          lengthMenu = list(c(10, 20, 30, 40, 50,-1),c("10", "20", "30", "40", "50","All")),
                                          scrollX = scrollXOpt),
                           extensions = 'Buttons',
                           rownames = FALSE,
                           ...)
    if (length(numericColNames) > 0){
      table <- table %>% DT::formatRound(columns = numericColNames,
                                     digits = numRound)
    }
    
    table
  }
```

```{r, include=FALSE}
# Init Step to make sure that the dependencies are loaded
htmltools::tagList(printTable(mtcars))
htmltools::tagList(ggplotly(ggplot()))
# Get the current figure size in pixels:
get_w <- function() {
  with(knitr::opts_current$get(c("fig.width", "dpi", "fig.retina")),
       fig.width*dpi/fig.retina)
}

get_h <- function() {
  with(knitr::opts_current$get(c("fig.height", "dpi", "fig.retina")),
       fig.height*dpi/fig.retina)
}
```
### Summary input information

The following table allows you to inspect the input information for the diversity analysis.

<p>&nbsp;</p>

```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))   
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
	
    seedatosum<-params$summBio$res1[[12]]
    
if("params"%in%ls()){ # we will download the document
  printTable(seedatosum, autoWidthOpt = TRUE, scrollXOpt = FALSE)
  }else{    
    DT::renderDT(printTable(seedatosum,
                        autoWidthOpt = FALSE, scrollXOpt = TRUE), server = FALSE)
  }
  
```

<p>&nbsp;</p>

### Summary diversity

The following table allows you to inspect the principal statistics for the diversity analysis.

<p>&nbsp;</p>

```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))   
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
	
    seedatosum<-params$summBio$res1[[1]]    
if("params"%in%ls()){ # we will download the document
  printTable(seedatosum, autoWidthOpt = TRUE, scrollXOpt = FALSE)           
  }else{    
    DT::renderDT(printTable(seedatosum,
                        autoWidthOpt = FALSE, scrollXOpt = TRUE), server = FALSE)
  }
  
```
<p>&nbsp;</p>

### Heatmap of distance matrix
  
  This plot allows the user to visualize the closeness or distance between genotypes.

<p>&nbsp;</p>
```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))	
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	
if("params" %in%ls()){ # we will download the document
	p=params$heat
	p
}else{
	plotly::renderPlotly({		
	p=params$heat	
	p
})
}
```

<p>&nbsp;</p>

### Diversity information by genotype
  
  This table allows the user to see statistics by genotypes.

<p>&nbsp;</p>
```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))
  }else{
    load("result.RData")	
  }
}, error = function(e) {
  shinyjs::hide()
}))
		seedatosgen<-params$summBio$res1[[11]]
    
if("params"%in%ls()){ # we will download the document
	printTable(seedatosgen, autoWidthOpt = TRUE, scrollXOpt = FALSE,colNames = colnames(seedatosgen))           
  }else{    
    DT::renderDT(printTable(seedatosgen, colNames = colnames(seedatosgen),
                        autoWidthOpt = FALSE, scrollXOpt = TRUE), server = FALSE)
  }
  
```

<p>&nbsp;</p>
### Diversity information by markers
  
  This table allows the user to see statistics by markers.

<p>&nbsp;</p>
```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))
  }else{
    load("result.RData")	
  }
}, error = function(e) {
  shinyjs::hide()
}))
		seedatosmark<-params$summBio$res1[[10]]
    
if("params"%in%ls()){ # we will download the document
  printTable(seedatosmark, autoWidthOpt = TRUE, scrollXOpt = FALSE,colNames = colnames(seedatosmark))           
  }else{    
    DT::renderDT(printTable(seedatosmark,colNames = colnames(seedatosmark),
                        autoWidthOpt = FALSE, scrollXOpt = TRUE), server = FALSE)
  }
  
```

<p>&nbsp;</p>

<p>&nbsp;</p>

### AMOVA

 Is a powerful tool that can help support hypotheses of population structure due to clonal reproduction or isolation without making assumptions about Hardy-Weinberg equilibrium. We have shown that we can reject the Ho
 of random mating between the two populations and have strong evidence that these populations are significantly differentiated at all stratifications.

<p>&nbsp;</p>

```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))   
  }else{
    load("resultPopStr.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	seeamova=as.data.frame(params$amovaT)
	seeamova=cbind(rownames(seeamova),seeamova)	
	colnames(seeamova)=c("source","Df","SumOfSqs","MS","F","Pr.F","Sigma" ,"PercVar","Phi")
	if("params" %in%ls()){ # we will download the document
	  printTable(seeamova, autoWidthOpt = TRUE, scrollXOpt = FALSE,
           colNames = colnames(seeamova))
	}else{
	  DT::renderDT(printTable(seeamova,
                        autoWidthOpt = FALSE, scrollXOpt = TRUE,
                        colNames = colnames(seeamova)), server = FALSE)
	}
    

```
<p>&nbsp;</p>

### Population structure (Fst) 

<p>&nbsp;</p>

```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))   
  }else{
    load("resultPopStr.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	seepop=as.data.frame(params$popstr)
	if("params" %in%ls()){ # we will download the document
	  printTable(seepop, autoWidthOpt = TRUE, scrollXOpt = FALSE)
	}else{
	  DT::renderDT(printTable(seepop,
                        autoWidthOpt = FALSE, scrollXOpt = TRUE), server = FALSE)
	}    

```

<p>&nbsp;</p>

### Multidimensional scaling plot 2D
  
  This plot allows the user to visualize the closeness or distance between genotypes to check if the population structure was as expected.

<p>&nbsp;</p>
```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))	
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	
if("params" %in%ls()){ # we will download the document
	p=params$mds2
	p
}else{
	plotly::renderPlotly({		
	p=params$mds2	
	p
})
}
```

<p>&nbsp;</p>

### Multidimensional scaling plot 3D
  
  This plot allows the user to visualize the closeness or distance between genotypes to check if the population structure was as expected.

<p>&nbsp;</p>
```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))	
  }else{
    load("result.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	
if("params" %in%ls()){ # we will download the document
	p3=params$mds3
	p3
}else{
	plotly::renderPlotly({		
	p3=params$mds3	
	p3
})
}
```

### MDS table  

<p>&nbsp;</p>

```{r, results='asis'}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))   
  }else{
    load("resultPopStr.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))
    
	seemds=as.data.frame(params$summBio$res2[[1]])
	#colnames(seemds)=c("Genotype","Factor1","Factor2","Factor3","Cluster")
	if(!is.null(params$summBio$res1[[9]])){				
		q_df <- as.data.frame(params$summBio$res1[[9]])
		q_df$Gen <- rownames(q_df)
		seemds$Gen <- as.character(seemds$Gen)
        q_df$Gen <- as.character(q_df$Gen)
		seemds <- dplyr::left_join(seemds, q_df, by = "Gen")
		colnames(seemds)[1]<-"Genotype"
	}
	
	if("params" %in%ls()){ # we will download the document
	  printTable(seemds, autoWidthOpt = TRUE, scrollXOpt = FALSE,colNames = colnames(seemds))
	}else{
	  DT::renderDT(printTable(seemds,colNames = colnames(seemds),
                        autoWidthOpt = FALSE, scrollXOpt = TRUE), server = FALSE)
	}    

```

<p>&nbsp;</p>


<p>&nbsp;</p>

### Dendogram
  
  This plot allows the user to visualize in one way the groupings of genotypes.

<p>&nbsp;</p>
```{r, results='asis',fig.width=14, fig.height=14}
suppressWarnings(tryCatch({
  if(file.exists(normalizePath("./data/result.RData"))){
    load(normalizePath("./data/result.RData"))	
  }else{
    load("result.RData")	
  }
}, error = function(e) {
  shinyjs::hide()
}))
	
if("params" %in%ls()){ # we will download the document
	params$dend
}else{
	if (figparams$typeclust=="rectangular"){
		shiny::renderPlot({
			params$dend
		},width = 950,height = 850)
	}else{
		shiny::renderPlot({
			params$dend
		},width = 950,height = 850)
	}
}
```


